\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-06-11 paper/RDF validation requirements/RDF validation requirements.tex
abstract

\begin{gcotable}
property & $\top$ & position & - & 1-23 & range & - \\
class & 1-23 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
class & 1-23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
\end{gcotable}

@@

>>>>

\begin{gcotable}
class & NumberPlayersPerWorldCupTeam & - & - & $\geq$1, $\leq$23 & $\sqcap$ & - \\
class & $\geq$1 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
class & $\leq$23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
\end{gcotable}

@@

\subsection{Constraining Elements of Constraint Types}

\begin{itemize}
  \item Constraints of 64\% of all constraint type can be expressed using logical constructs from description logics.
	\item We developed a vocabulary and for each constraint type we identified constraining elements to represent constraints of any constraint type.

	\item In most cases, it is sufficient to use only 1 logical construct
	\item Some combinations of logical constructs can be simplified to 1 logical construct which can be used in terms of syntactic sugar
  \item constraints of the majority of the constraint types can be expressed logically by description logics
	\item constraints of all constraint types can be expressed by constraining elements
	\item For 1 constraint types, there can be multiple constraining elements
	\item the validation of each constraining element has to be implemented
	\item We use SPARQL as extension mechanism to express constraints of 3 constraint types which cannot be expressed otherwise as they are too complex to represent them using a high-level constraint language
\end{itemize}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{lll}
           \multicolumn{1}{l}{\textbf{Constraint Type}} & \multicolumn{1}{l}{\textbf{DL}} & \multicolumn{1}{l}{\textbf{Constraining Elements}}			 
    \\ \midrule

*Subsumption & $\sqsubseteq$ & sub-classes \\
*Class Equivalence & $\equiv$ & equivalent classes \\
*Sub Properties & $\sqsubseteq$ & sub-properties \\
*Property Domain & $\exists$, $\sqsubseteq$ & domain \\
*Property Range & $\sqsubseteq$, $\forall$ & range \\
*Inverse Object Properties & inverse & \\
%*Symmetric Object Properties & $\equiv$, inverse & symmetric \\
*Symmetric Object Properties & symmetric &  \\
%*Asymmetric Object Properties & $\sqsubseteq$, inverse & asymmetric \\
*Asymmetric Object Properties & asymmetric &  \\
%*Reflexive Object Properties & $\exists$, $\sqsubseteq$ & \textcolor{green}{reflexive} \\
*Reflexive Object Properties & reflexive &  \\
%*Irreflexive Object Properties & $\exists$, $\neg$, $\sqsubseteq$ & irreflexive \\
*Irreflexive Object Properties & reflexive, $\neg$ & irreflexive \\
Disjoint Properties & $\sqsubseteq$, $\neg$ & $\ne$ \\
Disjoint Classes & $\sqcap$, $\sqsubseteq$ & $\ne$ \\
Context-Sp. Property Groups & $\sqcap$ & property groups \\
Context-Sp. Inclusive OR of P. & $\sqcup$ & inclusive or \\
Context-Sp. Inclusive OR of P. Groups & $\sqcup$, $\sqcap$ & inclusive or, \\
                                                          && property groups \\
Recursive Queries & - & recursive \\
Individual Inequality & $\ne$ & \\
*Equivalent Properties & $\equiv$ & equivalent properties \\
Property Assertions & = or $\ne$ & \\
Data Property Facets & - & XSD or SPARQL constraining facets \\
                        && examples: regex, xsd:pattern, ... \\
Literal Pattern Matching & - & regex or xsd:pattern \\
Negative Literal Pattern Matching & - & regex or xsd:pattern, $\neg$ \\ 
*Object Property Paths & $\sqsubseteq$ & property paths \\
*Intersection & $\sqcap$ & intersection \\
*Disjunction & $\sqcup$ & disjunction \\
*Negation & $\neg$ & negation \\
*Existential Quantification & $\exists$ & existential quantification \\
*Universal Quantification & $\forall$ & universal quantification \\
*Minimum Unqualified Cardinality & $\geq$ & \\
*Minimum Qualified Cardinality & $\geq$ & \\
*Maximum Unqualified Cardinality & $\leq$ & \\
*Maximum Qualified Cardinality & $\leq$ & \\
*Exact Unqualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
*Exact Qualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
*Transitive Object Properties & $\sqsubseteq$ & transitive \\
Context-Sp. Exclusive OR of P. & $\neg$, $\sqcap$, $\sqcup$ & XOR \\
Context-Sp. Exclusive OR of P. Groups & $\neg$, $\sqcap$, $\sqcup$ & XOR, $\sqcap$ \\
Allowed Values & $\sqcup$ & allowed \\
Not Allowed Values & $\sqcup$, $\neg$ & not allowed \\
%Literal Ranges & $\geq$, $\leq$, $\sqcap$ &  \\ 
Literal Ranges & - & xsd:minInclusive \\
               & & xsd:maxInclusive \\
%Negative Literal Ranges & $\geq$, $\leq$, $\sqcap$, $\neg$ & \\  
Negative Literal Ranges & - & xsd:minInclusive \\
                        & & xsd:maxInclusive \\
Required Properties & $\exists$ & required \\

    \bottomrule
    \end{tabular}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{lll}
           \multicolumn{1}{l}{\textbf{Constraint Type}} & \multicolumn{1}{l}{\textbf{DL}} & \multicolumn{1}{l}{\textbf{Constraining Elements}}			 
    \\ \midrule

Optional Properties & $\exists$, $\sqsubseteq$ & optional \\
Repeatable Properties & $\geq$ & repeatable \\
Negative Property Constraints & $\neg$, $\exists$ & negative properties \\
*Individual Equality & = & \\
*Functional Properties & functional & \\ 
*Inverse-Functional Properties & inverse, functional & inverse functional \\
*Value Restrictions & $\exists$ & value restriction \\
*Self Restrictions & $\exists$ & self restriction \\
Primary Key Properties & inverse, functional & keyfor or primary key \\
*Class-Specific Property Range & $\sqsubseteq$, $\exists$, $\neg$ & range \\
*Class-Sp. Reflexive Object P. & reflexive & \\
Membership in Controlled Vocabularies & $\forall$, $\sqcap$, $\sqcup$ & membership in \\
  && controlled vocabularies \\
IRI Pattern Matching & - & IRI pattern matching \\
Literal Value Comparison & $>$ or $\geq$ or $<$ or & \\
                         & $\leq$ or = or $\ne$ & \\
Ordering & - & order \\ 
Validation Levels & - & validation level \\ 
String Operations & - & SPARQL string operations \\ 
  && examples: STRLEN, \\ 
	&& SUBSTR, CONTAINS \\
Context-Specific Valid Classes & - & context-specific valid classes \\
Context-Specific Valid Properties & - & context-specific valid properties \\
Default Values & - & default values \\
Mathematical Operations & - & example: multiplication \\
Language Tag Matching & - & language tag matching \\
Language Tag Cardinality & - & language tag minimum cardinality, \\
                            && language tag maximum cardinality, \\
													  && language tag exact cardinality \\
Whitespace Handling & - & whitespace \\
HTML Handling & - & html \\
Conditional Properties & $\sqsubseteq$ & conditional \\
Recommended Properties & - & recommended \\
Handle RDF Collections & - & actions on RDF collections \\
Value is Valid for Datatype & - & value is valid for datatype \\
Use Sub-Super Relations in Validation & - & not redundant \\
*Cardinality Shortcuts & & optional \& non-repeatable, \\
                       & & optional \& repeatable \\
											 & & mandatory \& non-repeatable \\
											 & & mandatory \& repeatable \\
Aggregations & - & aggregations \\
                 && e.g., count \\
*Class-Specific Irreflexive Object Properties & reflexive, $\neg$ & irreflexive \\
Provenance & - & provenance \\   
Data Model Consistency & - & SPARQL \\    
Structure & - & SPARQL \\  
Labeling and Documentation & - & SPARQL \\   
Vocabulary & - & vocabulary \\  
HTTP URI Scheme Violation & - & HTTP URI scheme violation \\

    \bottomrule
    \end{tabular}
    \end{center}
\end{table}

### 2015-06-11 paper/paper 2/dc-2015.tex
abstract

\maketitle
\vspace{-3em}
\section*{Abstract}
Increasingly, various domains adopt Linked Data principles
and seek for ways to ensure data quality by validating RDF data according to predefined constraints,
in particular, as many communities are used to have this functionality in the XML world.
%XML Schema is the standard language to formulate constraints to validate XML documents.
%For RDF, however, there are several constraint languages - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
To validate RDF data and to formulate constraints, several languages exist or are currently developed,
but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
% Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text. In abstract and introduction, we just give general idea so at such points we better focus on flow.  
Based on our work in the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}, 
we published by today 81 types of constraints that are required by various stakeholders for data applications.
%The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
%%(whether expressible in description logics or not).
%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.

The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
(2) As current high-level constraint languages do not support all constraint types, 
we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
to intermediately represent constraints 
%as an intermediate generic representation 
which enables transformations between semantically equivalent constraints.
(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.

>>>>

\maketitle
\vspace{-3em}
\section*{Abstract}
Increasingly, various domains adopt Linked Data principles
and seek for ways to ensure data quality by validating RDF data according to predefined constraints,
in particular, as many communities are used to have this functionality in the XML world.
%XML Schema is the standard language to formulate constraints to validate XML documents.
%For RDF, however, there are several constraint languages - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
To validate RDF data and to formulate constraints, several languages exist or are currently developed,
but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
% Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text. In abstract and introduction, we just give general idea so at such points we better focus on flow.  
Based on our work in the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}, 
we published by today 81 types of constraints that are required by various stakeholders for data applications.

As there are already five promising constraint languages, 
our purpose is not to invent yet another constraint language.
But as non of the current constraint languages does support all constraint types, 
we developed a lightweight vocabulary to intermediately represent constraints of any constraint type in a generic way.
Even though, this vocabulary is not considered to be a constraint language,
constraints represented by the proposed vocabulary are intuitively understandable 
as their structure is based on RDF terminology. 
As we developed a vocabulary to represent constraint of any constraint type, 
we are therefore able to provide a basic terminology and classification system for RDF constraints 
to lay the ground for discussions on RDF validation.

When using the developed vocabulary to intermediately represent constraints,
depending on the individual type of constraint particular constraining elements can be applied.
We base these constraining elements on formal logic.
As constraints of 2/3 of all constraint types are expressible by logical constructs from description logics,
we may use logical constructs as constraining elements.
In order to be able to support all constraint types, however,
we determined intuitive constraining elements in natural language like \emph{conditional properties}, \emph{allowed values}, and \emph{language tag minimum cardinality}.
Constraints of the constraint type \emph{required properties}, e.g., can be expressed by the existential quantifier $\exists$ or more intuitively using the constraining element \emph{required properties}.

As SPARQL is generally seen as the method of choice to validate data according to certain constraints and
as RDF data can be validated on constraints of any constraint type by means of SPARQL,
we use SPIN, a SPARQL-based way to validate RDF data, as implementation language 
to actually execute the validation of RDF data.
Thereby, constraints may either be 
(1) expressed by domain specific constraint languages like OWL 2 and DSP or
(2) represented generically by the proposed vocabulary.

%The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
%%(whether expressible in description logics or not).
%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.

%The main contributions of this paper are:
%(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
%(2) As current high-level constraint languages do not support all constraint types, 
%we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
%(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
%to intermediately represent constraints 
%%as an intermediate generic representation 
%which enables transformations between semantically equivalent constraints.
%(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.
